msAggr_sctransform-v1

### 2021-07-07 msAggr_seurat.Rmd

---
title: "msAggr_seurat-v1"
output: html_notebook
---

Creating new pipeline using seurat v4.0.2 available 2021.06.08

@@

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(clustree)
```
store session info
```{r}
sink("msAggr_seurat-v1.20210608")
sessionInfo()
sink()
```

@@

```{r}
source("msAggr_AnalysisCode/read_10XGenomics_data.R")

```{r}
setwd("../cellRanger/") # temporarily changing wd only works if you run the entire chunk at once
data_file.list <- read_10XGenomics_data(sample.list = c("LSKm2", "CMPm2", "MEPm", "GMPm"))
seurat.object.data<-Read10X(data_file.list)
```

```{r}
seurat.object<- CreateSeuratObject(counts = seurat.object.data, min.cells = 3, min.genes = 200, project = projectName)
```

@@

```{r}
remove(seurat.object.data)
```

@@

remove low quality cells
require: nFeature_RNA between 200 and 4000 (inclusive)
--require: percent.mt <5--???

```{r}
print(paste("original object:", nrow(seurat.object@meta.data), "cells", sep = " "))
seurat.object <- subset(seurat.object, 
												subset = nFeature_RNA >=200 & 
													nFeature_RNA <= 4000
												)
print(paste("new object:", nrow(seurat.object@meta.data), "cells", sep = " "))
```

@@

```{r}
seurat.object <- FindVariableFeatures(seurat.object, selection.method = "vst", nfeatures = 2000)
```

Find variable features
```{r fig.width = 5, fig.height = 2}
seurat.object <- FindVariableFeatures(seurat.object, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(seurat.object), 10)
plot1 <- VariableFeaturePlot(seurat.object)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2

@@

```{r}
all.genes <- rownames(seurat.object)
seurat.object <- ScaleData(seurat.object, features = all.genes)
```

@@

```{r}
seurat.object <- RunPCA(seurat.object, features = VariableFeatures(object = seurat.object))
```

```{r fig.width=4, fig.height=4}
VizDimLoadings(seurat.object, dims = 1:6, nfeatures = 10, reduction = "pca", ncol = 2)
```

DimPlot colored by orig.ident
```{r}
DimPlot(seurat.object, reduction = "pca", group.by = "orig.ident")
```

Let's put in a concerted effort to pick the right dimensionality using the newest software

```{r}
jackstraw.dim <- 40
seurat.object <- JackStraw(seurat.object, num.replicate = 100, dims = jackstraw.dim) #runs ~50 min
seurat.object <- ScoreJackStraw(seurat.object, dims = 1:jackstraw.dim)
save.image(paste0(projectName, ".RData"))
```

Draw dim.reduction plots

```{r}
JackStrawPlot(seurat.object, dims = 25:36)
```
```{r, figures-side, fig.show='hold', out.width="50%"}
ElbowPlot(seurat.object, ndims = 50)
percent.variance(seurat.object@reductions$pca@stdev)
```
Number of PCs describing X% of variance

```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
paste0("Num pcs for 80% variance:", length(which(cumsum(tot.var) <= 80)))
paste0("Num pcs for 85% variance:", length(which(cumsum(tot.var) <= 85)))
paste0("Num pcs for 90% variance:", length(which(cumsum(tot.var) <= 90)))
paste0("Num pcs for 95% variance:", length(which(cumsum(tot.var) <= 95)))

@@

# KNN dimensional reduction
## Dim36

36 PCs describe 95% percent of variance, but one of the earlier critiques was that too many dimensions were included. Best way to deal with this is probably to try a couple of different ones. Let's start with 36 because I dare to rebel.

```{r}
seurat.object <- FindNeighbors(seurat.object, dims = 1:36)
seurat.object <- FindClusters(seurat.object, resolution = 0.5)
```

Generate UMAP data
```{r}
seurat.object <- RunUMAP(seurat.object, dims = 1:36) # took < 1 min
```

Plot the results
```{r}
DimPlot(seurat.object, 
				reduction = "umap"
				) + ggtitle("msAggr dim36 res0.5")

```{r}
DimPlot(seurat.object,
				reduction = "umap", 
				group.by = "orig.ident"
				) + ggtitle("msAggt dim36 orig.ident")
```

```{r}
saveRDS(seurat.object, file = "msAggr_dim36.rds")
```

## Dim24
36 dimensions looks very "swoopy". might have asked for too many dimensions. Will try dim = 24, which accounts for 90% of variance

```{r}
# seurat.object <- FindNeighbors(seurat.object, dims = 1:24)
# seurat.object <- FindClusters(seurat.object, resolution = 0.5)
# seurat.object <- RunUMAP(seurat.object, dims = 1:24)
```

Plot the results
```{r}
# DimPlot(seurat.object, 
# 				reduction = "umap"
# 				) + ggtitle("msAggr dim24 res0.5")

```{r}
# DimPlot(seurat.object,
# 				reduction = "umap", 
# 				group.by = "orig.ident"
# 				) + ggtitle("msAggt dim24 orig.ident")
```

```{r}
# saveRDS(seurat.object, file = "msAggr_dim24.rds")
```

## KNN conclusion
24 vs 36 dimensions doesn't seem to make that much difference RE overall relationships between cells. Should probbaly create two separate objects and try a few plotting methods, but will start by focusing on 36 dimensions.

# Cluster analysis

Will proceed with dim = 36 and do clustering analysis with a range of clusters. Later can do the tree-based over-clustering assessment

```{r}
seurat.object <- readRDS("msAggr_dim36.rds")
```

## Generate cluster profiles
Picking range of resolutions
```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	seurat.object <- FindClusters(seurat.object, resolution = x)
}
seurat.object <- RunUMAP(seurat.object, dims = 1:36)
```

Plot the clustering over different resolutions. Going to need a much better color palette, or try mixing in some different symbols

```{r}
# saveRDS(seurat.object, file = "msAggr_dim36.rds")
```

@@

# Why are clusters so unstable?
Differences could include:
* cells in each population (cellranger v6 includes more cells than cellranger v1, especially in MEP)
* dimensionality is incorrect
* ScaleData didnt account for regression factors (e.g., "nCounts_RNA" or "nFeatures_RNA")
* Incorrect normalization/scaling method
* Clustering is too strict or not strict enough
* neighborhood analysis used wrong parameters
* Should include mitoC filter (there's a chunk of MEP w/ mitoC @ ~40%)
* SCTransform accounts better for sources of variability

>>>>

---
title: "msAggr_seurat"
output: html_notebook
---

Creating new pipeline using seurat v4.0.2 available 2021.06.23  
Important notes:

* FILTERING on `percent.mt`, but NOT regressing on `percent.mt`
* Regressing on `nCounts_RNA` and `nFeature_RNA`

@@

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```
store session info
```{r}
sink("msAggr_seurat-v1.20210623")
sessionInfo()
sink()
```

@@

```{r}
source("msAggr_AnalysisCode/read_10XGenomics_data.R")
source("msAggr_AnalysisCode/PercentVariance.R")
```

```{r}
setwd("../cellRanger/") # temporarily changing wd only works if you run the entire chunk at once
data_file.list <- read_10XGenomics_data(sample.list = c("LSKm2", "CMPm2", "MEPm", "GMPm"))
data.object<-Read10X(data_file.list)
```

```{r}
seurat.object<- CreateSeuratObject(counts = data.object, min.cells = 3, min.genes = 200, project = projectName)
```

@@

```{r}
remove(data.object)
```

@@

remove low quality cells
require: nFeature_RNA between 200 and 4000 (inclusive)
require: percent.mt <= 5

```{r}
print(paste("original object:", nrow(seurat.object@meta.data), "cells", sep = " "))
seurat.object <- subset(seurat.object, 
												subset = nFeature_RNA >=200 & 
													nFeature_RNA <= 4000 & 
													percent.mt <= 5
												)
print(paste("new object:", nrow(seurat.object@meta.data), "cells", sep = " "))
```

@@

Find variable features
```{r fig.width = 5, fig.height = 2}
seurat.object <- FindVariableFeatures(seurat.object, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(seurat.object), 10)
plot1 <- VariableFeaturePlot(seurat.object)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2
```

@@

```{r}
all.genes <- rownames(seurat.object)
seurat.object <- ScaleData(seurat.object, features = all.genes, vars.to.regress = c("nCount_RNA", "nFeature_RNA"))
```

@@

```{r}
seurat.object <- RunPCA(seurat.object, features = VariableFeatures(object = seurat.object))
```
Plot results
```{r fig.width=4, fig.height=4}
VizDimLoadings(seurat.object, dims = 1:6, nfeatures = 10, reduction = "pca", ncol = 2)
```

DimPlot colored by orig.ident
```{r}
DimPlot(seurat.object, reduction = "pca", group.by = "orig.ident")
```
Let's put in a concerted effort to pick the right dimensionality using the newest software
```{r}
# jackstraw.dim <- 40
# seurat.object <- JackStraw(seurat.object, num.replicate = 100, dims = jackstraw.dim) #runs ~50 min
# seurat.object <- ScoreJackStraw(seurat.object, dims = 1:jackstraw.dim)
# save.image(paste0(projectName, ".RData"))
```
Draw dim.reduction plots
```{r}
# JackStrawPlot(seurat.object, dims = 25:36)
```
```{r, figures-side, fig.show='hold', out.width="50%"}
ElbowPlot(seurat.object, ndims = 50)
percent.variance(seurat.object@reductions$pca@stdev)
```
Number of PCs describing X% of variance
```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
paste0("Num pcs for 80% variance:", length(which(cumsum(tot.var) <= 80)))
paste0("Num pcs for 85% variance:", length(which(cumsum(tot.var) <= 85)))
paste0("Num pcs for 90% variance:", length(which(cumsum(tot.var) <= 90)))
paste0("Num pcs for 95% variance:", length(which(cumsum(tot.var) <= 95)))

@@

## Add cluster IDs from Seurat v1

Exported cell IDs for clusters 3, 17, 10, 11 from Seurat v1. Will add these IDs as a metadata column.  
Create column "clust.ID" and populate with 0's. Then import IDs for clusters
```{r}
clust3.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster3cellIDs.txt", col.names = "clust03")
clust3.cells <- sapply(clust3.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust17.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster17cellIDs.txt", col.names = "clust17")
clust17.cells <- sapply(clust17.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust10.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster10cellIDs.txt", col.names = "clust10")
clust10.cells <- sapply(clust10.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust11.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster11cellIDs.txt", col.names = "clust11")
clust11.cells <- sapply(clust11.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
```

Add new metadata column and map new ids
```{r}
seurat.object@meta.data['clust.ID'] <- 0
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust3.cells] <- 3
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust17.cells] <- 17
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust10.cells] <- 10
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust11.cells] <- 11
```

do numbers make sense (we don't expect the count to b exactly the same as the numbers in the original cluster)?
```{r}
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 10,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 11,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 17,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 3,])
```

make enough sense!

# DGE

Let's do some cluster analyses and see if we can find these populations in our new analysis.
## Ideal resolution...? (Is this a thing?)
### Color palette
```{r}
color.palette <- c(
	"coral",
	"chartreuse4",
	"goldenrod1",
	"cadetblue1",
	"burlywood",
	"brown",
	"brown1",
	"blue",
	"blue4",
	"azure3",
	"aquamarine",
	"antiquewhite",
	"cadetblue",
	"gold3",
	"black",
	"darkgreen",
	"deeppink",
	"darkviolet",
	"darkturquoise",
	"darkslategray",
	"darksalmon",
	"darkorchid1",
	"darkolivegreen2",
	"forestgreen",
	"dodgerblue",
	"green",
	"lightpink",
	"lightcoral",
	"khaki1",
	"maroon",
	"peru",
	"lightseagreen",
	"lightsalmon",
	"plum",
	"moccasin",
	"tan",
	"tan1", 
	"red", 
	"purple",
	"khaki4",
	"black", 
	"plum4"
)
```

# Total var 90%
## Neighborhood and umap
set total.var <- 90%
```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 90))

seurat.object <- FindNeighbors(seurat.object, dims = 1:ndims)
seurat.object <- FindClusters(seurat.object, resolution = 0.5)
seurat.object <- RunUMAP(seurat.object, dims = 1: ndims)

saveRDS(seurat.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
```
Plot UMAP

```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	seurat.object <- FindClusters(seurat.object, resolution = x)
}
```

```{r}
for (meta.col in colnames(seurat.object@meta.data)){
	if(grepl(pattern = ("RNA_snn_res"), x = meta.col)==TRUE){
		myplot <- DimPlot(seurat.object, 
											group.by = meta.col,
											reduction = "umap", 
											cols = color.palette
											) + 
			ggtitle(paste0(projectName, " dim", ndims, "res", gsub("RNA_snn_res", "", meta.col) ))
		plot(myplot)
	}
}
```

For each resolution, what percentage of cells in each cluster are enriched for one of our clust.IDs?

Test: what percentage of each new clusterID matches one of the older clusters?
```{r}
for (meta.col in colnames(seurat.object@meta.data)){
	if(grepl(pattern = ("RNA_snn_res"), x = meta.col)==TRUE){
		new.clusters <- sort(as.numeric(levels(seurat.object@meta.data[[meta.col]])))
		enrich.df <- data.frame(matrix(ncol = 4, nrow = length(new.clusters)))
		colnames(enrich.df) <- c(3, 17, 10, 11)
		rownames(enrich.df) <- new.clusters
		meta.df <- seurat.object@meta.data
		for(row.id in rownames(enrich.df)){
			tot.clus <- nrow(meta.df[meta.df[[meta.col]] == row.id,])
			for(col.id in colnames(enrich.df)){
				num.x <- nrow(meta.df[(meta.df[[meta.col]] == row.id) & (meta.df$clust.ID == col.id),])
				pct.x <- as.integer(num.x / tot.clus *100)
				# print(pct.x)
				enrich.df[row.id, col.id] <- pct.x
			}
		}
		colnames(enrich.df) <- sapply(colnames(enrich.df), function(x) paste0("oldcluster", x))
		rownames(enrich.df) <- sapply(rownames(enrich.df), function(x) paste0("newcluster", x))
		xlsx::write.xlsx(enrich.df, file = paste0("PctOfNewClustersOverlappingOldClusters_", projectName, "_dim", ndims, ".xlsx"), sheetName = paste0(gsub("RNA_snn_", "", meta.col)), append = TRUE)
		print(enrich.df)
	}
}

```
Absolutely terrible overlap, no enrichment of any of these across the new clustering algorithm. Maybe should try 95% variation covered

## Find old cells on UMAP

time for the super scarey moment to see if the cells from seuratv1 still cluster together on in seurat v4

```{r fig.width = 4}
DimPlot(seurat.object,
				reduction = "umap",
				group.by = "clust.ID", 
				# split.by = "orig.ident",
				cols = c("gray", "orange", "blue", "red", "green"),)
```
```{r fig.width = 4}
DimPlot(seurat.object,
				reduction = "umap",
				group.by = "orig.ident", 
				split.by = "clust.ID",
				cols = c("gray", "orange", "blue", "red", "green"),)
```

# Total var 95%
## Neighborhood and umap
set total.var <- 95%
```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 95))

seurat.object <- FindNeighbors(seurat.object, dims = 1:ndims)
seurat.object <- FindClusters(seurat.object, resolution = 0.5)
seurat.object <- RunUMAP(seurat.object, dims = 1: ndims)

saveRDS(seurat.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
```
Plot UMAP

```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	seurat.object <- FindClusters(seurat.object, resolution = x)
}
```

For each resolution, what percentage of cells in each cluster are enriched for one of our clust.IDs?

Test: what percentage of each new clusterID matches one of the older clusters?
```{r}
for (meta.col in colnames(seurat.object@meta.data)){
	if(grepl(pattern = ("RNA_snn_res"), x = meta.col)==TRUE){
		new.clusters <- sort(as.numeric(levels(seurat.object@meta.data[[meta.col]])))
		enrich.df <- data.frame(matrix(ncol = 4, nrow = length(new.clusters)))
		colnames(enrich.df) <- c(3, 17, 10, 11)
		rownames(enrich.df) <- new.clusters
		meta.df <- seurat.object@meta.data
		for(row.id in rownames(enrich.df)){
			tot.clus <- nrow(meta.df[meta.df[[meta.col]] == row.id,])
			for(col.id in colnames(enrich.df)){
				num.x <- nrow(meta.df[(meta.df[[meta.col]] == row.id) & (meta.df$clust.ID == col.id),])
				pct.x <- as.integer(num.x / tot.clus *100)
				# print(pct.x)
				enrich.df[row.id, col.id] <- pct.x
			}
		}
		colnames(enrich.df) <- sapply(colnames(enrich.df), function(x) paste0("oldcluster", x))
		rownames(enrich.df) <- sapply(rownames(enrich.df), function(x) paste0("newcluster", x))
		xlsx::write.xlsx(enrich.df, file = paste0("PctOfNewClustersOverlappingOldClusters_", projectName, "_dim", ndims, ".xlsx"), sheetName = paste0(gsub("RNA_snn_", "", meta.col)), append = TRUE)
		print(enrich.df)
	}
}

```
Absolutely terrible overlap, no enrichment of any of these across the new clustering algorithm. Maybe should try 95% variation covered

## Find old cells on UMAP

time for the super scarey moment to see if the cells from seuratv1 still cluster together on in seurat v4

```{r fig.width = 2}
DimPlot(seurat.object,
				reduction = "umap",
				group.by = "clust.ID", 
				pt.size = .1,
				# split.by = "orig.ident",
				cols = c("gray", "orange", "blue", "red", "green"),)
```
```{r fig.width = 4}
DimPlot(seurat.object,
				reduction = "umap",
				group.by = "orig.ident", 
				split.by = "clust.ID",
				cols = c("gray", "orange", "blue", "red", "green"),)
```

### Gene expression of old clustrs on new map
Let's see if we can get some gene expression profiles on these...
```{r, fig.height=10, fig.width=18}
gene.list <- c("Gata1", "Gata2", "Pf4", "Dntt", "Mpo", "Meis1", "Irf8", "Elane", "Fli1", "Zfpm1")
VlnPlot(seurat.object, features = gene.list, group.by = "clust.ID", pt.size = 0.01, cols = c("gray", "orange", "blue", "red", "green"))
```

@@

# Why are clusters so unstable?
Differences could include:
* cells in each population (cellranger v6 includes more cells than cellranger v1, especially in MEP)
* dimensionality is incorrect
* ScaleData didnt account for regression factors (e.g., "nCounts_RNA" or "nFeatures_RNA")
* Did not consider cell cycle
* Incorrect normalization/scaling method
* Clustering is too strict or not strict enough
* neighborhood analysis used wrong parameters
* Should include mitoC filter (there's a chunk of MEP w/ mitoC @ ~40%)
* SCTransform accounts better for sources of variability

### 2021-07-07 noMtThreshold/msAggr_sctransform-v1.Rmd

---
title: "msAggr_sctransform-v1"
output: html_notebook
---

@@

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(clustree)
```
store session info
```{r}
sink("msAggr_sct-v1.20210615")
sessionInfo()
sink()
```

@@

@@

```{r}
remove(seurat.object.data)
```

@@

@@

@@

@@

```{r}
for (x in c("LSKm2", "CMPm2", "MEPm", "GMPm")){
	h = hist(seurat.object@meta.data[seurat.object@meta.data$orig.ident == x, 'percent.mt'], breaks = 30, plot = FALSE)
	h$density = h$counts/sum(h$counts)*100
	plot(h,freq=FALSE, main =  paste(x, "percent mitoC"), xlab = "percent mitoC", ylab = "Frequency")
}

>>>>

---
title: "msAggr_sctransform-v1"
output:
  html_document:
    df_print: paged
---

@@

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```
store session info
```{r}
sink("msAggr_sct-v1.20210615")
sessionInfo()
sink()
```

@@

########IS SCTRANSFORM MORE ROBUST FOR DIFFERENT SEQUENCING DEPTHS??#########

@@

```{r}
remove(object.data)
```

@@

## Save base object
```{r}
saveRDS(seurat.object, file = "msAggr_rawSeurat.rds")
```

@@

```{r}
DimPlot(seurat.object, group.by = "orig.ident", reduction = "umap")
```

@@

```{r}
fav.genes <- c("Gata1", "Gata2", "Pf4", "Dntt", "Mpo", "Meis1", "Irf8", "Elane", "Fli1", "Zfpm1", "proc")
```

```{r}
FeaturePlot(seurat.object, features = fav.genes, ncol = 3)
```

@@

```{r}
for (x in c("LSKm2", "CMPm2", "MEPm", "GMPm")){
	h = hist(seurat.object@meta.data[seurat.object@meta.data$orig.ident == x, 'percent.mt'], breaks = 30, plot = FALSE)
	h$density = h$counts/sum(h$counts)*100
	plot(h,freq=FALSE, main =  paste(x, "percent mitoC"), xlab = "percent mitoC", ylab = "Frequency")
}
```

# Why are clusters so unstable?
Differences could include:
* cells in each population (cellranger v6 includes more cells than cellranger v1, especially in MEP)
* --dimensionality is incorrect--
* ScaleData didnt account for regression factors (e.g., "nCounts_RNA" or "nFeatures_RNA")
* Incorrect normalization/scaling method
* --Clustering is too strict or not strict enough--
* neighborhood analysis used wrong parameters
* Should include mitoC filter (there's a chunk of MEP w/ mitoC @ ~40%)
* --SCTransform accounts better for sources of variability--

# Regress out cell cycle
One thing I've probably done in the past is regress out cell cycle factors. Did not do that here. Repeat analysis but include cell cycle regression.  
Cell cycle scoring comes after `RunPCA()`

Step 1: load in raw object
```{r}
seurat.object <- readRDS("msAggr_rawSeurat.rds")
```

Since `SCTransform()` is best for different correcting different sequencing depths, going to stick with that

The [Cell Cycle Regression Vignette](https://satijalab.org/seurat/articles/cell_cycle_vignette.html) says to do `NormalizeData()`, `FindVariableFeatures()`, `ScaleData()`, `RunPCA()`, `CellCycleScoring()`, then `RunPCA()` with s.genes and g2m.genes. It seems to be more complicated with `SCTransform()` because you don't want to normalize normalized data, but you need normalized data to properly run `CellCycleScoring()`. Found discussion board and [this](https://github.com/satijalab/seurat/issues/1679#issuecomment-557781838) is the answer that makes the most sense to me

```{r results='asis'}
# normalize data with SCTransform()
sample <- SCTransform(
  sample,
  assay = 'RNA',
  new.assay.name = 'SCT',
  vars.to.regress = c('percent.mt', 'nFeature_RNA', 'nCount_RNA')
)

# perform cell cycle analysis (make sure to specify the "assay" parameter
sample <- CellCycleScoring(
  sample,
  s.features = s.genes,
  g2m.features = g2m.genes,
  assay = 'SCT',
  set.ident = TRUE
)

# normalise again but this time including also the cell cycle scores
sample <- SCTransform(
  sample,
  assay = 'RNA',
  new.assay.name = 'SCT',
  vars.to.regress = c('percent.mt', 'nFeature_RNA', 'nCount_RNA', 'S.Score', 'G2M.Score')
)
```

so let's try this

```{r}
seurat.object <- SCTransform(seurat.object, assay = 'RNA', new.assay.name = "SCT", method = "glmGamPoi", vars.to.regress = c("nFeature_RNA", "nCount_RNA"))
```

Cell cycle scoring
```{r}
seurat.object <- CellCycleScoring(seurat.object, s.features = cc.genes$s.genes, g2m.features = cc.genes$g2m.genes, assay = 'SCT', set.ident = FALSE)
```
